Gaia identifies VFTS682 as the most massive runaway star known to date

### 2018-05-12 VFTS682.tex
incorporated comments on text from van der Marel more
added stephen

\author{M.~Renzo$^{1}$, S.~E.~de~Mink$^{1}$, D.~J.~Lennon$^{2}$,
  J. Bestenlehner$^{3}$,  F.~R.~Schneider$^5$, R.~.P.~van~der~Marel$^{6,7}$, J.~Vink$^{8}$ \SdM{et al.?} \\ \SdM{[ Alphabetical after Lennon. Possibly add further last-minute coauthors]},  }

  % S.~Justham$^{3,4}$,
%  A.~de~Koter$^{1}$ \todo{... add coauthors...} }

\affil{$^{1}$Astronomical Institute Anton Pannekoek, University of
    Amsterdam, 1098 XH Amsterdam, The Netherlands \\
    $^{2}$ ESA, European Space Astronomy Centre, Apdo. de Correos 78,
    E-28691 Villanueva de la Ca\~nada, Madrid, Spain \\
    $^3$ {Department of Physics and Astronomy, Hicks Building,
      Hounsfield Road, University of Sheffield, Sheffield S3 7RH, UK}\\
  %  $^{3}$ {School of Astronomy \& Space Science, University of the Chinese
   % Academy of Sciences, Beijing 100012, China}\\
    % $^4$ {National Astronomical Observatories, Chinese Academy of
     %  Sciences, Beijing 100012, China}\\
     $^5$ {Department of Physics, University of Oxford, Keble Road,
       Oxford OX1 3RH, UK} \\
     $^{6}$ {Space Telescope Science Institute, 3700 San Martin Drive,
       Baltimore, MD 21218, USA}\\
     $^{7}$ {Center for Astrophysical Sciences, Department of Physics \& Astronomy, Johns Hopkins University, Baltimore, MD 21218, USA}\\
     $^8$ {Armagh Observatory, College Hill, Armagh BT61 9DG, UK}
}

@@

\begin{table}[t]
\begin{center}
    \caption{Astrometric parameters for VFTS682. }
%
  \begin{tabular}{l|c|c}
  \tableline
\tableline
    Parameter & Value & Source\\ 
    \tableline
    RA \hfill[degree] &  \phantom{-}84.73 $\pm$  0.03 & \multirow{4}{*}{Gaia DR2}\\
    DEC \hfill [degree] & -69.07 $\pm$  0.05  & \\
    $\mu_\mathrm{RA}$  \hfill[$\mathrm{mas\ yr^{-1}}$] & \phantom{-0}1.84 $\pm$ 0.07 & \\
    $\mu_\mathrm{DEC}$  \hfill[$\mathrm{mas\ yr^{-1}}$] & \phantom{-0}0.78 $\pm$ 0.08& \\
    $\delta v_\mathrm{rad}$  \hfill[$\kms$] & \phantom{-0}30 $\pm$ 20 & \cite{bestenlehner:11}\\
\tableline
  \end{tabular}
  % \tablecomments{}
    \end{center}
  \label{tab:vfts682}
\end{table}

>>>>

\author{M.~Renzo$^{1}$, S.~E.~de~Mink$^{1}$, D.~J.~Lennon$^{2}$, J. Bestenlehner$^{3}$, S.~Justham$^{4,5}$, F.~R.~Schneider$^6$, R.~P.~van~der~Marel$^{7,8}$, J.~Vink$^{9}$ \SdM{et al.?} \\ \SdM{[ Alphabetical after Lennon. Possibly add further last-minute coauthors]},  }

  % ,
%  A.~de~Koter$^{1}$ \todo{... add coauthors...} }

\affil{$^{1}$Astronomical Institute Anton Pannekoek, University of
    Amsterdam, 1098 XH Amsterdam, The Netherlands \\
    $^{2}$ ESA, European Space Astronomy Centre, Apdo. de Correos 78,
    E-28691 Villanueva de la Ca\~nada, Madrid, Spain \\
    $^3$ {Department of Physics and Astronomy, Hicks Building,
      Hounsfield Road, University of Sheffield, Sheffield S3 7RH, UK}\\
   $^{4}$ {School of Astronomy \& Space Science, University of the Chinese
   Academy of Sciences, Beijing 100012, China}\\
    $^5$ {National Astronomical Observatories, Chinese Academy of
      Sciences, Beijing 100012, China}\\
     $^6$ {Department of Physics, University of Oxford, Keble Road,
       Oxford OX1 3RH, UK} \\
     $^{7}$ {Space Telescope Science Institute, 3700 San Martin Drive,
       Baltimore, MD 21218, USA}\\
     $^{8}$ {Center for Astrophysical Sciences, Department of Physics \& Astronomy, Johns Hopkins University, Baltimore, MD 21218, USA}\\
     $^9$ {Armagh Observatory, College Hill, Armagh BT61 9DG, UK}
}

@@

\begin{table}[t]
\begin{center}
    \caption{Astrometric parameters for VFTS682. }
%
  \begin{tabular}{l|c|c}
  \tableline
\tableline
    Parameter & Value & Source\\ 
    \tableline
    RA \hfill[degree] &  \phantom{-}84.73 $\pm$  0.03 & \multirow{4}{*}{Gaia DR2}\\
    DEC \hfill [degree] & -69.07 $\pm$  0.05  & \\
    $\mu_\mathrm{RA}$  \hfill[$\mathrm{mas\ yr^{-1}}$] & \phantom{-0}1.84 $\pm$ 0.07 & \\
    $\mu_\mathrm{DEC}$  \hfill[$\mathrm{mas\ yr^{-1}}$] & \phantom{-0}0.78 $\pm$ 0.08& \\
    $\delta v_\mathrm{rad}$  \hfill[$\kms$] & \phantom{-0}30 $\pm$ 20 & \cite{bestenlehner:11}\\
\tableline
  \end{tabular}
  \tablecomments{We truncate the errors on RA and DEC for the purpose
    of display. Readers are encouraged to consult the Gaia DR2 catalog
  for accurate values.}
    \end{center}
  \label{tab:vfts682}
\end{table}
